---
title: "Assignment #2"
format: html
editor: visual
---

```{r}

{r setup, include=FALSE}
knitr::opts_chunk$set(echo       = TRUE, 
                      fig.height = 3, 
                      fig.width  = 6,
                      fig.align  = "center")
ggplot2::theme_set(ggplot2::theme_bw())



```

```{r}

#| message: false
library(tidyverse)

library(lubridate)


```

## If statement included

```{r}


pos_na <- function(a,b){

if(length(a) == length(b)) 
  
{which (is.na(a) & is.na(b))}

else {print("The vectors are not the same length.")}
}


```

```{r}



x <- c(1, NA, 2) 
y <- c(NA, NA)
pos_na(x,y)
```

```{r}

a <- c(NA, NA, 2) 
b <- c(NA, NA, 2)
pos_na(a,b)


```

```{r}


c <- c(NA, 5, NA) 
d <- c(NA, NA, NA)
pos_na(c,d)


```

```{r}

e <- c(NA, NA, NA, 2, NA, 4, NA)
f <- c(NA, NA, 2, 4, 4, NA, NA)

pos_na(e,f)



```

```{r}

g <- c(1, NA, NA, 2, NA, 4, NA)
h <- c(NA, -5, 2, 4, 4, NA, 11)

pos_na(g,h)

```

```{r}





```

```{r}





```

## Question 2

Load the `wmata_ridership`{style="font-family: Monaco, Menlo, Consolas, \"Courier New\", monospace; font-size: 0.75rem; border-radius: 6px; background-color: rgb(242, 244, 244); border-color: rgb(232, 234, 236); padding: 0.125rem 0.25rem; color: rgb(199, 31, 35); font-variant-ligatures: normal; white-space-collapse: collapse;"} data frame into R from [https://dcgerard.github.io/stat_412_612/data/wmata_ridership.csvLinks to an external site.](https://dcgerard.github.io/stat_412_612/data/wmata_ridership.csv){.uri .external target="_blank" rel="noreferrer noopener" style="color: rgb(14, 104, 179); font-family: LatoWeb, \"Lato Extended\", Lato, \"Helvetica Neue\", Helvetica, Arial, sans-serif; font-size: 16px; font-variant-ligatures: normal; white-space-collapse: collapse;"}. For each month, calculate the proportion of rides made on a given day of the month. Then make box plots of ridership proportions by day of the week. But exclude any days from 2004 and 2005.

```{r}
#Read in the data properly.

wmata_data <- read.csv("Folder Data/wmata_ridership.csv")

head(wmata_data)

year("2004-01-01")

month("2004-01-01", label = TRUE)

wday("2004-01-01", label = TRUE)
```

```{r}

wmata_data|>
  mutate(wmata_data, Year = year(Date),
                     Month = month(Date),
                     Wday = wday(Date, label = TRUE)) -> wmata_data2

wmata_data2



```

```{r}
wmata_data2|>
  filter(!(Year %in% c(2004,2005))) -> wmata_data2

#Updated
wmata_data2

```

```{r}

wmata_data2|>
  group_by(Month,Wday)|>
  mutate(Proportion = Total/sum(Total))|>
  ungroup()-> wmata_data2

wmata_data2

```

```{r}

ggplot(wmata_data2, aes(x = Wday, y = Proportion)) +
  geom_boxplot()



```

## Question 3

```{r}

V <- c("Bears", "Lions", "Dolphins", "Eagles", "Bengals")


names(V) <- c("b", "l", "d", "e", "be")

V[c("b", "d", "be")]

```

## Subsetting with for loop

```{r}

V <- c("Bears", "Lions", "Dolphins", "Eagles", "Bengals")
V

print(V[1])



```

```{r}

#Subsetting for loop

V <- c("Bears", "Lions", "Dolphins", "Eagles", "Bengals")

for (i in c(1,3,5)) {
  print (V[i])
}





```

## Subsetting with positive indices

```{r}

V <- c("Bears", "Lions", "Dolphins", "Eagles", "Bengals")


V[c(1, 3, 5)]






```

## Subsetting using negative indices

```{r}


V <- c("Bears", "Lions", "Dolphins", "Eagles", "Bengals")

V[-c(2,4)]



```

## Subsetting using logical indexing

```{r}

V <- c("Bears", "Lions", "Dolphins", "Eagles", "Bengals")

V[c(TRUE, FALSE, TRUE, FALSE, TRUE)]




```

## Question 4

## Parse

```{r}
records <- c(
  "Steve McQueen | 2020-01-15 | HR",
  "B. Smith | 15/02/2021 | FIN",
  "Carlos M | March 3, 2019 | IT",
  "D. Lee | 2018/07/30 | HR",
  "Alain Delon | 04-12-2020 | MKT"
)
records

  


```

## Parse into three separate variables

```{r}

HRData <- tibble(records = c( "Steve McQueen | 2020-01-15 | HR",
  "B. Smith | 15/02/2021 | FIN",
  "Carlos M | March 3, 2019 | IT",
  "D. Lee | 2018/07/30 | HR",
  "Alain Delon | 04-12-2020 | MKT"))
                 
HRData |>              
separate_wider_delim(records,
                     names = c("name", "hire_date", "dept"),
                     delim = "|")

  
  



```

## Convert dates

```{r}

ymd("2020-01-15")


dmy("15/02/2021")

mdy("March 3, 2019")

ymd("2018/07/30")

mdy("4-12-2020")

hire_date <- c("2020-01-15", "2021-02-15", "2019-03-03","2018-07-30", "2020-04-12")

hire_date
```

## Ordered factors

```{r}

x1 <- c("HR", "FIN", "IT", "HR", "MKT")

x1

dept_levels <- c("FIN", "HR", "IT", "MKT")

dept <- factor(x1, levels = dept_levels)

dept

summary(dept)
```

## Name of employees

```{r}






```

## Construct a data frame

```{r}

hire_date <- c ("2020-01-15","2021-02-15","2019-03-03","2018-07-30","2020-04-12")

dept <- c("FIN","HR","IT","MKT")

employee_name <- c("Steve McQueen", "B.Smith", "Carlos M", "D. Lee", "Alain Delon")


clean_df <- data.frame(
  hire_date = c("2020-01-15","2021-02-15","2019-03-03","2018-07-30","2020-04-12"), 
  dept = c("HR","FIN","HR","IT","MKT"), 
  employee_name = c("Steve McQueen", "B.Smith", "Carlos M", "D. Lee", "Alain Delon")
)

clean_df
```

## Add a new variable: years worked

```{r}






```
